From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-13 Pi+/paper/finite.tex
Define the coxeter relations and closure

\begin{definition}
  Let $A$ be a type and $R : A \to A \to \UU$ a binary relation on $A$. The group $G$ presented by
  $\langle A ; R \rangle$ is given by the set-quotient of the free group $F(A)$ by the normal closure $N_{R}$, or
  equivalently, as the coequaliser
  \[\begin{tikzcd}
      FR && FA && G
      \arrow[shift right=2, from=1-1, to=1-3]
      \arrow[shift left=2, from=1-1, to=1-3]
      \arrow[two heads, from=1-3, to=1-5]
    \end{tikzcd}\]
\end{definition}

@@

\begin{definition}[Coxeter relation]
  \begin{align*}
    & \mathsf{cancel} : (n \cons n \cons \nil) \cx \nil \\
    & \mathsf{swap} : (\suc[k] < n) \to (n \cons k \cons \nil) \cx (k \cons n \cons \nil) \\
    & \mathsf{braid} : (\suc[n] \cons k \cons \suc[n] \cons \nil) \cx (n \cons \suc[k] \cons n \cons \nil)
  \end{align*}
\end{definition}

The type $\Sn$ is defined as the set-quotient of $\List(\Fin[n])$ by the congruence closure of $\cx$.

\begin{definition}[$\Sn$]
  \(\Sn \defeq \quot{\List(\Fin[n])}{\cx^{\ast}}\)
\end{definition}

>>>>

\begin{definition}
  Let $A$ be a type and $R : A \to A \to \UU$ a binary relation on $A$. The group $G$ presented by
  $\langle A ; R \rangle$ is given by the set-quotient of the free group $F(A)$ by the normal closure $N_{R}$ of $R$, or
  equivalently, as the coequaliser
  \[\begin{tikzcd}
      FR && FA && G
      \arrow[shift right=2, from=1-1, to=1-3]
      \arrow[shift left=2, from=1-1, to=1-3]
      \arrow[two heads, from=1-3, to=1-5]
    \end{tikzcd}\]
\end{definition}

@@

\begin{definition}[$\cox$]
  \begin{align*}
    \cancel
    & : \forall n \to (n \cons n \cons \nil) \cox \nil \\
    \swap
    & : \forall k, n \to (\suc[k] < n) \to (n \cons k \cons \nil) \cox (k \cons n \cons \nil) \\
    \braid
    & : \forall k, n \to (\suc[n] \cons k \cons \suc[n] \cons \nil) \cox (n \cons \suc[k] \cons n \cons \nil) \\
  \end{align*}
\end{definition}

We define $\cox*$ as the congruence closure of $\cox$.

\vc{This could be simplified a bit depending on our formalisation.}

\begin{definition}[$\cox*$]
  \begin{align*}
    \reflr{\cox}
    & : \forall w \to w \cox* w \\
    \symr{\cox}
    & : \forall w_{1}, w_{2} \to w_{1} \cox* w_{2} \to w_{2} \cox* w_{1} \\
    \transr{\cox}
    & : \forall w_{1}, w_{2}, w_{3} \to  w_{1} \cox* w_{2} \to w_{2} \cox* w_{3} \to w_{1} \cox* w_{3} \\
    \congrf{\cox}{\append}
    & : \forall w_{1}, w_{2}, w_{3}, w_{4} \to  w_{1} \cox* w_{2} \to w_{3} \cox* w_{4} \to w_{1} \append w_{3} \cox* w_{2} \append w_{4} \\
    \relr{\cox}
    & : \forall w_{1}, w_{2} \to w_{1} \cox w_{2} \to w_{1} \cox* w_{2} \\
  \end{align*}
\end{definition}

The type $\Sn$ is defined as the set-quotient of $\List(\Fin[n])$ by $\cox*$.
q
\begin{definition}[$\Sn$]
  \(\Sn \defeq \quot{\List(\Fin[n])}{\cox*}\)
\end{definition}
